
\section{Realizable Potentials}
\label{sec:realizable}

\subsection{Activation-Potential Calculations}
First define the {\it dual} of a function $f: \R \to \R$ is defined to be 
%
\[ \widehat{f}(\rho) = \expt_{X,Y \sim N(\rho)}[f(X)f(Y)],\]
%
where $N(\rho)$ is the bivariate normal distribution with $X, Y$ unit variance and $\rho$ covariance. This is as in \cite{DanielyFS16}.
%
\begin{lemma}\label{rotLem}
Let $\mathcal{M} = S^{d-1}$ and $\sigma$ be our activation function, then $\widehat{\sigma}$ is the corresponding potential function.
\end{lemma}

\begin{proof}
If $u, v$ have norm 1 and if $X$ is a standard Gaussian in $\R^d$, then note that $X_1 = u^TX$ and $X_2 = v^TX$ are both standard Gaussian variables in $\R^1$ and the covariance is $E[X_1X_2] = u^Tv$. 

Therefore, the dual function of the activation gives us the potential function.
\begin{align*}
\expt_{X}[\sigma(u^TX)\sigma(v^TX)] & =
\expt_{X,Y \sim N(u^Tv)}[\sigma(X)\sigma(Y)] \\
& = \widehat{\sigma}(u^Tv).
\end{align*}
\end{proof}

By Lemma \ref{rotLem}, the calculations of the activation-potential
for the sign, ReLU, Hermite, exponential functions are given in
\cite{DanielyFS16}. For the Gaussian and Bessel activation functions,
we can calculate directly. In both case, we notice that we may write
the integral as a product of integrals in each dimension. Therefore,
it suffices to check the following 1-dimensional identities.
\begin{align*}
  & \int_{-\infty}^\infty
    \sqrt{2}e^{x^2/4}e^{-(x-\theta)^2}\sqrt{2}e^{x^2/4}e^{-(x-w)^2} \frac{1}{\sqrt{2\pi}} e^{-x^2/2}\, dx \\
  & \qquad = \sqrt{\frac{2}{\pi}}\int_{-\infty}^\infty
    e^{-(x-\theta)^2}e^{-(x-w)^2} \, dx = e^{-(\theta -w)^2/2}
\end{align*}
\begin{align*}
& \int_{-\infty}^\infty (\frac{2}{\pi})^{3/2}e^{x^2/2}K_0(|x-\theta|)K_0(|x-w|)  \frac{1}{\sqrt{2\pi}} e^{-x^2/2}\, dx \\
& \qquad 
= \int_{-\infty}^\infty \frac{2}{\pi^2}K_0(|x-\theta|)K_0(|x-w|) \, dx
  = e^{-|\theta -w|}
\end{align*}


The last equality follows by Fourier uniqueness and taking the Fourier transform of both sides, which are both equality $\sqrt{2/\pi}(\omega^2+1)^{-1}$. 


\subsection{Characterization Theorems}


\tranreal*

\begin{proof}
Since $\Phi$ is square-integrable, its Fourier transform exists. Let $h(x) = \FT^{-1}(\sqrt{\FT(\Phi)})(x)$ and this is well-defined since the Fourier transform was non-negative everywhere and the Fourier inverse exists since $\sqrt{\FT(\Phi)}(x)$ is square-integrable. Now, let $\sigma(x,w) = (2\pi)^{1/4}e^{x^2/4}h(x-w)$. Realizability follows by the Fourier inversion theorem:
%
\begin{align*}
    \expt_{X \sim N}[\sigma(X,w)\sigma(X,\theta)]  &= \int_{\R^n} h(x-w)h(x-\theta) \, dx \\
    &= \int_{\R^n} h(x)h(x-(\theta-w)) \, dx \\
    &= \FT^{-1}(\FT(h\ast h)(\theta -w)) \\
    &= \FT^{-1}(\FT(h)^2(\theta - w)) \\
    &= \FT^{-1}(\FT(\Phi)(\theta - w)) \\
    &= \Phi(\theta - w) 
\end{align*}
 
Note that $\ast$ denotes function convolution.
\end{proof}



When our relevant space is $\mathcal{M} = S^{d-1},$ we let
$\Pi_\mathcal{M}$ be the projection operator on $\mathcal{M}$. The
simplest way to define the gradident on
$S^{d-1}$ is $\nabla_{S^{d-1}} f(x) = \nabla_{\R^d} f(x/\|x\|)$, where
$\| \cdot \|$ denotes the $l_2$ norm and $x \in S^{d-1}$. 
The Hessian and Laplacian are analogously defined and the subscripts
are usually dropped where clear from context.
%
\begin{restatable}{theorem}{rotreal}
\label{thm:rotReal}
Let $\mathcal{M} = S^{d-1}$ and $\Phi(\theta,w) = f(\theta^Tw)$. Then,
$\Phi$ is realizable if $f$ has non-negative Taylor coefficients, $c_i
\geq 0$ , and the corresponding activation $\sigma(x) = \sum_{i=1}^\infty \sqrt{c_i} h_i(x)$
converges almost everywhere, where $h_i(x)$ is the i-th Hermite polynomial.
\end{restatable}


\begin{proof}
By \ref{rotLem} and due to the orthogonality of hermite polynomials, if $f = \sum_i a_i h_i$, where $h_i(x)$ is the i-th Hermite polynomial, then
%
\[\widehat{f}(\rho) = \sum_{i} a_i^2 \rho^i\]

Therefore, any function with non-negative taylor coefficients is a valid potential function, with the corresponding activation function determined by the sum of hermite polynomials, and the sum is bounded almost everywhere by assumption.
\end{proof}

\subsection{Further Characterizations}

To apply Theorem~\ref{thm:tranReal}, we need to check that the Fourier transform of our function is non-negative. Not only is this is not straightforward to check, many of our desired potentials do not satisfy this criterion. In this section, we would like to have a stronger characterization of realizable potentials, allowing us to construct realizable potentials that approximates our desired potential.
 
\begin{definition}
Let $\Phi$ be a positive semidefinite function if for all $x_1,...,x_n$, the matrix $A_{ij} = \Phi(x_i - x_j)$ is positive semidefinite. 
\end{definition}

\begin{lemma}\label{lem:psd}
Let $\mathcal{M} = \R^d$ and $\Phi(\theta, w) = f(\theta-w)$ is is realizable, then it is positive semidefinite.
\end{lemma}

\begin{proof}
If $\Phi$ is realizable, then there exists $\sigma$ such that  $\Phi(\theta, w) =  \expt_{X \sim N}[\sigma(X, w)\sigma(X, \theta)]$. For $x_1,...,x_n$, we note that the quadratic form:
\begin{align*}
\sum_{i,j} \Phi(x_i,x_j) v_i v_j 
& = \sum_{i,j} \expt_{X \sim N}[\sigma(X, x_i)\sigma(X, x_j)] v_i v_j 
 = \expt_{X \sim N}\left[\left(\sum_{i}v_i \sigma(X , x_i) \right)^2\right] \geq 0
\end{align*}

Since $\Phi$ is translationally symmetric, we conclude that $\Phi$ is positive semidefinite.
\end{proof}


\begin{definition}
A potential $\Phi$ is $\FT$-integrable if it is square-integrable and $\FT({\Phi}(\omega))$ is integrable, where $\FT$ is the standard Fourier transform.
\end{definition}

\begin{lemma}\label{intReal}
Let $w(x) \geq 0$ be a positive weighting function such that $\int_a^b w(x) \, dx$ is bounded. If $\Phi_x$ is a parametrized family of $\FT$-integrable realizable potentials, then, $\int_a^b w(x) \Phi_x$ is $\FT$-integrable realizable.
\end{lemma}

\begin{proof}
Let $\Phi = \int_a^b w(x) \Phi_x$. From linearity of the Fourier transform and $\int_a^b w(x)\, dx$ is bounded, we know that $\Phi$ is $\FT$-integrable. Since $\Phi_x$ are realizable, they are positive definite by Lemma~\ref{lem:psd} and by Bochner's theorem, their Fourier transforms are non-negative. And since $w(x) \geq 0$, we conclude by linearity and continuity of the Fourier transform that $\FT(\Phi) \geq 0$. By Theorem \ref{thm:tranReal}, we conclude that $\Phi$ is realizable.
\end{proof}



\begin{lemma}\label{baseConstruct}
Let $\mathcal{M} = \R^d$ for $d \equiv 3 \mod 4$. Then, for any $\epsilon, t > 0$, there exists a $\FT$-integrable realizable $\Phi$ such that for $t \geq r > \epsilon$, $\Phi^{(d-1)}(r) = t -r$ and for $ r \leq \epsilon$, $\Phi^{(d-1)}(r) = \frac{t-\epsilon}{\epsilon}r$. Furthermore, $\Phi^{(k)}(r) = 0$ for $r > t$ for all $0 \leq k \leq d$.
\end{lemma}

\begin{proof}
Our construction is based on the radial activation function $h_t(x, \theta) = \bf{1}_{\|\theta - x\| \leq t/2}$, which is the indicator in the disk of radius $t/2$. This function, when re-weighted correctly as $\sigma_t(x,\theta) =  (2\pi)^{1/4} e^{x^2/4}h_t(x,\theta)$ gives rise to a radial potential function that is simply the convolution of $h_t$ with itself, measuring the volume of the intersection of two spheres of radius $t$ centered at $\theta$ and $w$.
%
\begin{align*}
\Phi_t(\theta, w) & = \expt_X[\sigma_t(X,\theta)\sigma_t(X,w)]
= \begin{cases}
C\int_{\|\theta - w\|/2}^{t/2} ((t/2)^2 - x^2)^{(d-1)/2} \, dx & \|\theta - w\| \leq t\\
0 & \textrm{ otherwise.}
\end{cases}
\end{align*}
%
Therefore, as a function of $r=\|\theta - w \|$, we see that when $r \leq t$, $\Phi_t(r) = C\int_{r/2}^{t/2} ((t/2)^2-x^2)^{(d-1)/2} \, dx$ and $\Phi_t'(r) = -C'((t/2)^2-(r/2)^2)^{(d-1)/2}$. Since $d \equiv 3 \mod 4$, we notice that $\Phi_t'$ has a positive coefficient in the leading $r^{d-1}$ term and since it is a function of $r^2$, it has a zero $r^{d-2}$ term. Therefore, we can scale $\Phi_t$ such that 
\begin{align*}
\Phi_t^{(d-1)}(r) = \begin{cases}
r & r \leq t\\
0 & \textrm{ otherwise.}
\end{cases} 
\end{align*}

$\Phi_t$ is clearly realizable and now we claim that it is $\FT$-integrable. First, $\Phi_t$ is bounded on a compact set so it is square-integrable. Now, since $\Phi_t = h_t \ast h_t$ can be written as a convolution, $\FT(\Phi_t) = \FT(h_t)^2$. Since $h_t$ is square integrable, then by Parseval's, $\FT(h_t)$ is square integrable, allowing us to conclude that $\Phi_t$ is $\FT$-integrable.

Now, for any $\epsilon > 0$, let us construct our desired $\Phi$ by taking a positive sum of $\Phi_t$ and then appealing to Lemma \ref{intReal}. Consider
%
\[\Phi(r) = \int_{\epsilon}^{t} \frac{1}{x^2}\Phi_x(r) \, dx\]

First, note that the total weight $\int_\epsilon^t \frac{1}{x^2}$ is bounded. Then, when $r \geq t$, since $\Phi_x(r) = 0$ for $x \leq t$, we conclude that $\Phi^{(k)}(r) = 0$ for any $k$. Otherwise, for $\epsilon < r < t$, we can apply dominated convergence theorem to get
\begin{align*}
\Phi^{(d-1)}(r) = \int_{\epsilon}^r \frac{1}{x^2}\Phi_x^{(d-1)}(r) \, dx + \int_{r}^t \frac{1}{x^2} \Phi_x^{(d-1)}(r) \, dx
 = 0 + \int_r^t \frac{r}{x^2} \, dx = 1 -r/t 
\end{align*}

Scaling by $t$ gives our desired claim. For $r\leq \epsilon$, we integrate similarly and scale by $t$ to conclude.
\end{proof}

\begin{lemma}\label{transConstruct}
Let $\mathcal{M} = \R^d$ for $d \equiv 3 \mod 4$ and let $\Phi(r)$ be a radial potential. Also, $\Phi^{(k)}(r) \geq 0$ and $\Phi^{(k+1)}(r)\leq 0$ for all $r > 0$ and $k \geq 0 $ even, and $\lim_{r \to \infty} \Phi^{(k)}(r) = 0$ for all $0 \leq k \leq d$. 

Then, for any $\epsilon > 0$, there exists a $\FT$-integrable realizable potential $\overline{\Phi}$  such that $\overline{\Phi}^{(k)}(r) = \Phi^{(k)}(r)$ for all $0 \leq k \leq d-1$ and $r \geq \epsilon$. Furthermore, we have $\overline{\Phi}^{(d-1)}(r) \geq 0$ for all $r  > 0$ and $\overline{\Phi}^{(k)}(r) \geq 0$ and $\overline{\Phi}^{(k+1)}(r)\leq 0$ for all $r > 0$ and $d - 3 \geq k \geq 0 $ even.

Lastly, for $r < \epsilon$ and $0 \leq k \leq d-1$, $|\overline{\Phi}^{(d-1-k)}(r)| \leq |\Phi^{(d-1-k)}(\epsilon)| + \sum_{j=1}^k \frac{(\epsilon - r)^{k-j+1}}{(k-j+1)!} |\Phi^{(d-j)}(\epsilon)|$
\end{lemma}

\begin{proof}
By Lemma \ref{baseConstruct}, we can find $\Phi_t$ such that
\begin{align*}
\Phi_t^{(d-1)} = \begin{cases}
\frac{t-\epsilon}{\epsilon } r & 0 \leq r \leq \epsilon \\
t - r & \epsilon < r \leq t \\
0 & r > t
\end{cases}
\end{align*}

Furthermore, $\Phi_t^{(k)}(r) = 0$ for $r > t$ for all $0 \leq k \leq d$.
Therefore, we consider 
%
\[\overline{\Phi}(r) = \int_{\epsilon}^\infty \Phi^{(d+1)}(x) \Phi_x(r) \, dx\] 

Note that this is a positive sum with $\int_{\epsilon}^\infty \Phi^{(d+1)}(x) \, dx = -\Phi^{(d)}(\epsilon) < \infty$. By the non-negativity of our summands, we can apply dominated convergence theorem and Fubini's theorem to get
\begin{align*}
\overline{\Phi}^{(d-1)}(r) & = \int_{\epsilon}^\infty  \Phi^{(d+1)}(x) (\Phi_x^{(d-1)}(r)) \, dx \\
& = \int_{r}^\infty  \Phi^{(d+1)}(x) (\Phi_x^{(d-1)}(r)) \, dx \\
& = \int_r^\infty \Phi^{(d+1)}(x) \int_r^x 1 \, dy \,dx  \\
& = \int_r^\infty \int_y^\infty \Phi^{(d+1)}(x) \, dx \, dy = \int_r^\infty  -\Phi^{(d)}(y) \, dy \\
& = \Phi^{(d-1)}(r)
\end{align*}

Now, since $\overline{\Phi}^{(d-1)}(r) = \Phi^{(d-1)}(r)$ for $r\geq \epsilon$ and $\lim_{r\to\infty} \overline{\Phi}^{(k)}(r) = \lim_{r\to\infty} {\Phi}^{(k)}(r) = 0$ for $0 \leq k \leq d-1$, repeated integration gives us our claim. 

Finally, for the second claim, notice that for $r \leq \epsilon$, we get
\begin{align*}
\overline{\Phi}^{(d-1)}(r) = \int_{\epsilon}^\infty  \Phi^{(d+1)}(x) (\Phi_x^{(d-1)}(r)) \, dx
=  r \int_\epsilon^\infty \Phi^{(d+1)}(x) \frac{x - \epsilon}{\epsilon} \, dx = Cr  
\end{align*}

Note that our constant $C \geq 0$ since the summands are non-negative. Therefore, we conclude that $\overline{\Phi}^{(d-1)}(r) \geq 0$ for all $r > 0$. Repeated integration and noting that $\lim_{r\to\infty} \overline{\Phi}^{(k)}(r) = 0$ for $0 \leq k \leq d-1$ gives us our claim.

Lastly, we prove the last claim of the theorem with induction on $k$. This holds trivially for $k = 0$ since $\overline{\Phi}^{(d-1)}(r) \leq \overline{\Phi}^{(d-1)}(\epsilon) = \Phi^{(d-1)}(\epsilon)$ for $r \leq \epsilon$. Then, assume we have the inequality for $k < d-1$. By integration, we have
\begin{align*}
|\overline{\Phi}^{(d-k-2)}(r)| & \leq |\overline{\Phi}^{(d-k-2)}(\epsilon)| + \int_r^\epsilon |\overline{\Phi}^{(d-1 -k)}(y)| \, dy \\
& \leq |\overline{\Phi}^{(d-k-2)}(\epsilon)| + \int_r^\epsilon |\overline{\Phi}^{(d-1 -k)}(\epsilon)| \, dy \\
& + \int_r^\epsilon \sum_{j=1}^k \frac{(\epsilon -y)^{k-j+1}}{(k-j+1)!}|\Phi^{(d-j)}(\epsilon)| \, dy \\
& \leq  |\overline{\Phi}^{(d-k-2)}(\epsilon)| + \sum_{j=1}^{k+1}  \frac{(\epsilon -y)^{k-j+2}}{(k-j+2)!}|\Phi^{(d-j)}(\epsilon)|
\end{align*}

Therefore, we conclude with induction.
\end{proof}

\almostharmreal*

\begin{proof}
Consider a potential of the form $\Phi(r) = p(r)e^{-\sqrt{\lambda}r}/r^{d-2}$. We claim that there exists a polynomial $p$ of degree $k = (d-3)/2$ with non-negative coefficients and $p(0) = 1$ such that $\Phi$ is $\lambda$-harmonic. Furthermore, we will also show along the way that $p(r) \leq (1+\sqrt{\lambda}r)^d$.

When $d = 3$, it is easy to check that $\Phi(r) = e^{(-\sqrt{\lambda})r}/r$ is our desired potential. Otherwise, by our formula for the radial Laplacian in $d$ dimensions, we want to solve the following differential equation:
%
\[\Delta \Phi =  \frac{1}{r^{d-1}} \frac{\partial}{\partial r} (r^{d-1} \frac{\partial \Phi}{\partial r}) =\lambda \Phi\]

Solving this gives us the following second-order differential equation on $p$
%
\[rp'' - (d-3+2\sqrt{\lambda}r)p' +\sqrt{\lambda} (d-3)p = 0\]

Let us write $p(r) = \sum_{i=0}^k a_i r^i$. Then, substituting into our differential equation gives us the following equations by setting each coefficient of $r^i$ to zero:

$r^i$:  $a_{i+1}(i+1)(i - (d-3)) = a_i \sqrt{\lambda} (2i-(d-3))$

$r^k:$ $(-2k +d-3)a_k = 0$

The last equation explains why we chose $k = (d-3)/2$, so that it is automatically zero. Thus, setting $a_0 = 1$ and running the recurrence gives us our desired polynomial. Note that the recurrence is valid and produces positive coefficients since $i < k  = (d-3)/2$. Our claim follows and $\Phi$ is $\lambda$-harmonic. And furthermore, notice that $a_{i+1} \leq \sqrt{\lambda} a_i \leq (\sqrt{\lambda})^{i+1}$. Therefore, $p(r) \leq (1+r\sqrt{\lambda})^d$. 

Lastly, we assert that $\Phi^{(j)}(r)$ is non-negative for $j$ even and non-positive for $j$ odd. To prove our assertion, we note that it suffices to show that if $\Phi$ is of the form $\Phi(r) = p(r) e^{-\sqrt{\lambda}r}/r^{l}$ for some $p$ of degree $k < l$ and $p$ has non-negative coefficients, then $\Phi'(r) = - q(r) e^{-\sqrt{\lambda}r}/r^{l+1}$ for some $q$ of degree $k+1$ with non-negative coefficients. 

Differentiating $\Phi$ gives:
%
\[\Phi' = \frac{e^{-r}}{r^{l+1}} (rp'(r) - (l + \sqrt{\lambda} r)p(r))\]

It is clear that if $p$ has degree $k$, then $q(r) = (l+\sqrt{\lambda} r)p(r) - rp'(r)$ has degree $k+1$, so it suffices to show that it has non-negative coefficients. Let $p_0,..., p_k$ be the non-negative coefficients of $p$. Then, by our formula, we see that 

$q_0 = l p_0$

$q_i = lp_i - ip_i + \sqrt{\lambda}p_{i-1} = (l-i)p_i + \sqrt{\lambda}p_{i-1}$ 

$q_{k+1} = \sqrt{\lambda} p_k$

Since $i \leq k < l$, we conclude that $q$ has non-negative coefficients. Finally, our assertion follows with induction since $\Phi^{(0)}(r)$ is non-negative and has our desired form with $k = (d-3)/2 < d-2$. By Lemma \ref{transConstruct}, our primary theorem follows, we can construct a realizable radial potential $\Phi_\epsilon(r)$ that is $\lambda$-harmonic when $r \geq \epsilon$ and has alternating-signed derivatives.

Lastly, we prove the following preliminary bound on $\Phi_\epsilon^{(k)}(r)$ when $k \leq d$: $|\Phi_\epsilon^{(k)}(r)| \leq 3(2d + \epsilon \sqrt{\lambda})^{2d}\epsilon^{-2d}  $ for all $0 \leq k \leq d-1$. First, notice that by the results of Lemma~\ref{transConstruct}, $\Phi_\epsilon^{(k)}(r)$ is monotone and $\lim_{r\to\infty}\Phi_\epsilon^{(k)}(r) = 0$. So, it follows that we just have to bound $|\Phi_{\epsilon}^{(k)}(0)|$. From our construction, $\Phi_{\epsilon}^{(k)}(\epsilon) = p_k(\epsilon)e^{-\sqrt{\lambda}\epsilon}\epsilon^{2-d-k}$, for some polynomial $p_k$. Furthermore, from our construction, we have the recurrence $p_{k}(\epsilon) = (d-2+k + \sqrt{\lambda}\epsilon)p_{k-1}(\epsilon) - \epsilon p_{k-1}'(\epsilon)$. Therefore, we conclude that for $k \leq d$, $p_k(\epsilon) \leq (2d + \sqrt{\lambda} \epsilon)^kp_0(\epsilon) \leq  (2d + \sqrt{\lambda} \epsilon)^k(1+\sqrt{\lambda}\epsilon)^d \leq (2d + \sqrt{\lambda}\epsilon)^{2d}$. 

Therefore, we can bound
 $|\Phi_\epsilon^{(k)}(\epsilon)| \leq (2d + \sqrt{\lambda}\epsilon)^{2d}\epsilon^{-2d}$. Finally, by Lemma~\ref{transConstruct}, 
\begin{align*}
|\Phi_{\epsilon}^{(d-1-k)}(0)| 
& \leq |\Phi_{\epsilon}^{(d-1-k)}(\epsilon)| + \sum_{j=1}^k \frac{(\epsilon )^{k-j+1}}{(k-j+1)!} |\Phi^{(d-j)}(\epsilon)| \\
& \leq (2d + \sqrt{\lambda}\epsilon)^{2d}\epsilon^{-2d} (1 + \sum_{j=1}^k \frac{\epsilon^{k-j+1}}{(k-j+1)!}) \\
& \leq (2d + \sqrt{\lambda}\epsilon)^{2d}\epsilon^{-2d} e^{\epsilon} \leq 3(2d + \sqrt{\lambda}\epsilon)^{2d}\epsilon^{-2d} 
\end{align*}

And for $r \geq \epsilon$, we see that $|\Phi_\epsilon(r)| = |\Phi(r)| \leq |p(r)|\frac{e^{-\sqrt{\lambda}r}}{r^{d-2}} = (1+r\sqrt{\lambda})^de^{-\sqrt{\lambda}r}r^{2-d}$. And $|\Phi_\epsilon'(r)| = |\Phi'(r)| \leq |p_1(r)| \frac{e^{-\sqrt{\lambda} r}}{r^{d-1}} \leq (d+\sqrt{\lambda}r)(1+ r\sqrt{\lambda})^de^{-\sqrt{\lambda} r} r^{1-d}$.


Finally, we consider the normalized potential: $\widetilde{\Phi}_\epsilon = {\Phi}_\epsilon/{\Phi}_\epsilon(0)$. Note that since ${\Phi}_\epsilon$ is monotonically decreasing, we can lower bound ${\Phi}_\epsilon(0) \geq {\Phi}_\epsilon(\epsilon) \geq e^{-\sqrt{\lambda}}$. Therefore, we can derive the following upper bounds: $|\widetilde{\Phi}_\epsilon^{(k)}(r)| \leq 3(2d + \sqrt{\lambda})^{2d} \epsilon^{-2d}e^{\sqrt{\lambda}}$ and for $r \geq \epsilon$, $|\widetilde{\Phi}_\epsilon(r)| \leq (1+r\sqrt{\lambda})^de^{\sqrt{\lambda}(1-r)}r^{2-d}$ and its derivative is bounded by $|\widetilde{\Phi}_\epsilon'(r)| \leq (d+\sqrt{\lambda}r)(1+ r\sqrt{\lambda})^de^{\sqrt{\lambda}(1- r)} r^{1-d}$.


And lastly, we derive some lower bounds on $\widetilde{\Phi}_\epsilon$ and the first derivative when $r \geq \epsilon$, by using the upper bound on $\Phi_\epsilon(0)$: $\widetilde{\Phi}_\epsilon(r) \geq {\Phi}_\epsilon(r)(2d+\sqrt{\lambda})^{-2d}\epsilon^{2d}/3  \geq e^{-\sqrt{\lambda}r}r^{2-d}(2d+\sqrt{\lambda})^{-2d}\epsilon^{2d}/3$. For the derivative, we get
 $|\widetilde{\Phi}_\epsilon'(r)| \geq e^{-\sqrt{\lambda}r}r^{1-d}(2d+\sqrt{\lambda})^{-2d}\epsilon^{2d}/3$.
\end{proof}


\begin{lemma}\label{3dlambdaharmonic}
The lambda-harmonic radial potential $\Phi(r) = e^{-r}/r$ in $3$-dimensions is realizable by the activation 
$\sigma(r) = K_1(r)/r$.
\end{lemma}

\begin{proof}
The activation is obtained from the potential function by first taking its Fourier transform, then taking its square root, and then taking the inverse fourier transform. Since the functions in consideration are radially symmetric the Fourier transform $F(y)$ of $f(x)$ (and inverse) are obtained by the Hankel Transfom $y F(y) = \int_0^\infty x f(x) J_{1/2} (xy) \sqrt{xy} dx$. Plugging $f(x) = e^{-x}/x$, from the Hankel tranform tables we get $yF(y) = cy/(1+y^2)$ giving $F(y) = cy/(1+y^2)$. So we wish to find the inverse Fourier transform for $1/\sqrt{1+y^2}$. The inverse $f(x)$ is given by $xf(x) = \int_0^\infty y F(y) J_{1/2} (xy) \sqrt{xy} dy = cK_1(x)$. So $\sigma(r) = K_1(r)/r$.
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "icmlpaper2017.tex"
%%% End: